Approximation as Differentiation

### 2025-04-16 appendix/notes/cmon-enriched.tex
More tweaks.

\noindent There exists an enriched version of the Yoneda embedding, namely a functor $\Yoneda_{\mathscr{V}}:
\cat{C} \to \Func{\cat{C}^\op}{\mathscr{V}}_{\mathscr{V}}$ sending objects $X$ to the enriched hom-functor
$\Yoneda_{\mathscr{V}}(X) = \Hom{\cat{C}}{-}{X}: \cat{C}^\op \to \mathscr{V}$ and providing a family of
morphisms $(\Yoneda_{\mathscr{V}})_{X,Y}: \Hom{\cat{C}}{X}{Y} \to
\Hom{\Func{\cat{C}^\op}{\mathscr{V}}_{\mathscr{V}}}{\Hom{\cat{C}}{-}{X}}{\Hom{\cat{C}}{-}{Y}}$.

The enriched Yoneda lemma says that for any $\mathscr{V}$-enriched presheaf $F$ and any object $X \in \cat{C}$
the hom-object of natural transformations between the $\mathscr{V}$-enriched presheaf $\Hom{\cat{C}}{-}{X}$
and $F$, which also lives in $\mathscr{V}$, is isomorphic to $F(X)$:

>>>>

\noindent There exists an enriched version of the Yoneda embedding, namely a functor $\Yoneda_{\mathscr{V}}:
\cat{C} \to \Func{\cat{C}^\op}{\mathscr{V}}_{\mathscr{V}}$, which is itself $\mathscr{V}$-enriched, sending
objects $X$ to the $\mathscr{V}$-enriched hom-functor $\Yoneda_{\mathscr{V}}(X) = \Hom{\cat{C}}{-}{X}:
\cat{C}^\op \to \mathscr{V}$ and morphisms $f: X \to Y$ in $\cat{C}$ to $\mathscr{V}$-natural transformations
$\Yoneda_{\mathscr{V}}(f): \Hom{\cat{C}}{-}{X} \naturalto \Hom{\cat{C}}{-}{Y}$ acting at each component as
post-composition with $f$.

The enriched Yoneda lemma says that for any $\mathscr{V}$-enriched presheaf $F$ and any object $X \in
\cat{C}$, the hom-object of $\mathscr{V}$-natural transformations (which also lives in $\mathscr{V}$) between
the $\mathscr{V}$-enriched presheaf $\Hom{\cat{C}}{-}{X}$ and $F$ is isomorphic to $F(X)$:
